\sang{YESTERDAY}
\begin{multicols}{2}
\spvers{Yesterday all my troubles seemed so far away.\\
Now it looks as though they're here to stay:\\
Oh, I believe in yesterday! \\
\\}
\spvers{
Suddenly l'm not half the man I used to be \\
There's a shadow hanging over me. \\
Oh, yesterday came suddenly. \\
\\}
\spvers{
Why she had to go, I don't know, \\
she wouldn't say. \\
I said something wrong, \\
Now I long for yesterday. \\
}
\spvers{
Yesterday love was such an easy game to play \\
Now I need a place to hide away. \\
Oh I believe in yesterday! \\
Mmmm.................. \\
Oh I believe in yesterday! \\
}
\end{multicols}
\sang{MY BONNIE}
\begin{multicols}{2}
\spvers{
My Bonnie is over the ocean, \\
My Bonnie is over the sea, \\
My Bonnie is over the ocean, \\
Oh! Bring back my Bonnie to me. \\
}
\sprefreng{
Bring back, bring back, \\
Bring back my Bonnie to me, to me, \\
Bring back, bring back \\
Oh! Bring back my Bonnie to me. \\
}
\spvers{
Oh, Blow, ye winds, over the ocean, \\
And blow, ye winds, over the sea; \\
Oh, Blow ye winds, over the ocean, \\
And bring back my Bonnie to me. \\
}
\sprefreng{Bring back, bring back....\\}
\spvers{
Last night as I lay on my pillow, \\
Last night as I lay on my bed; \\
Last night as I lay on my pillow \\
I dream'd that my Bonnie was dead. \\
}
\sprefreng{Bring back, bring back....\\}
\spvers{
The winds have blown over the ocean, \\
The winds have blown over the sea; \\
the winds have blown over the ocean, \\
And brought back my Bonnie to me. \\
}
\sprefreng{Bring back, bring back....\\}
\end{multicols}
